---
title: "shinyLumi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_shinyLumi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyLumi)
```

# Loading data

```{r,eval=FALSE}

idatPath <- path to your folder contain idat file
methylumi::methylumIDAT(getBarcodes(path=idatPath), idatPath=idatPath)

```

# Beta values

$\beta=\frac{M}{M+U+100}$ where M and U denote the methylated and unmethylated signals respectively. For each array we have a lot of beta value since there are a number of beads in each array.


# Functions

Two export functions in this package. One for drawing density plot of beta values from different methylation arrays, another is corresponding shiny app.

## methylumiDensity()

**mldat** is the MethyLumiSet object contains methylation information

**Sample_sheet** is the sheet about relationship between methylation arrays and sample groups. Not always given.

Rest of the parameters are simply for plotting format options.
